---
title: "[ECODEVT] Data Analysis"
author: "Group 1"
date: today
format: 
  html:
    toc: true
    theme: united
    embed-resources: true
knitr:
  opts_chunk: 
    warning: false
    message: false
editor: visual
---

# Paper Details

## **Research Question**

Are the current Philippine education system and alternative training programs adequate to cater to the educational and physiological needs of persons with disabilities (PWDs) in Barangay CAA?

## **Statement of Hypothesis**

Ho: The regular schooling and alternative learning system for PWDs in Barangay CAA is accessible.

Ha: The regular schooling and alternative learning system for PWDs in Barangay CAA is inaccessible.

## **Research Objectives**

-   Illustrate the school attendance of PWDs

-   Identify the barriers experienced by PWDs in the education system

-   Evaluate the accessibility of regular schools and ALS programs in accommodating various disabilities

------------------------------------------------------------------------

# Preliminary Steps

## Install and load the necessary data sets

```{r}

```

## Install and load R packages

Make sure that the system has access to the *tidyverse*, *psych,* and *readxl* packages needed for data management, and the *car, broom, lmtest,* *whitestrap,* and *wooldridge* needed for regression models.

```{r}
# Install three packages that are not yet installed
if(!("tidyverse" %in% installed.packages()[,"Package"])) install.packages("tidyverse")
if(!("readxl" %in% installed.packages()[,"Package"])) install.packages("readxl")
if(!("psych" %in% installed.packages()[,"Package"])) install.packages("psych")
if(!("car" %in% installed.packages()[,"Package"])) install.packages("car")
if(!("broom" %in% installed.packages()[,"Package"])) install.packages("broom")
if(!("lmtest" %in% installed.packages()[,"Package"])) install.packages("lmtest")
if(!("whitestrap" %in% installed.packages()[,"Package"])) install.packages("whitestrap")
if(!("wooldridge" %in% installed.packages()[,"Package"])) install.packages("wooldridge")

library(tidyverse)
library(readxl)
library(psych)
library(car)
library(broom)
library(lmtest)
library(whitestrap)
library(wooldridge)
library(ggplot2)
```

------------------------------------------------------------------------

## OBJECTIVE 1 \| Illustrate the school attendance of PWDs

```{r}
# Install three packages that are not yet installed
if(!("tidyverse" %in% installed.packages()[,"Package"])) install.packages("tidyverse")
if(!("readxl" %in% installed.packages()[,"Package"])) install.packages("readxl")
if(!("psych" %in% installed.packages()[,"Package"])) install.packages("psych")
if(!("car" %in% installed.packages()[,"Package"])) install.packages("car")
if(!("broom" %in% installed.packages()[,"Package"])) install.packages("broom")
if(!("lmtest" %in% installed.packages()[,"Package"])) install.packages("lmtest")
if(!("whitestrap" %in% installed.packages()[,"Package"])) install.packages("whitestrap")
if(!("wooldridge" %in% installed.packages()[,"Package"])) install.packages("wooldridge")

library(tidyverse)
library(readxl)
library(psych)
library(car)
library(broom)
library(lmtest)
library(whitestrap)
library(wooldridge)
library(ggplot2)
```

------------------------------------------------------------------------

```{r}
educ_data <- read_excel("C:/Users/admin/OneDrive/Documents/RSTUDIO/ecodevt v24 database Barangay CAA (1).xlsx", sheet = "MAIN")
```

### \[1.1\] School attendance

```{r}
psych::describe(educ_data$schoolattendance_dummy)
```
```{r}
count<-table(educ_data$schoolattendance_dummy)
```
```{r}
library(ggplot2)
library(dplyr)  # For data manipulation

# Assuming 'count' is your data frame with counts
count_schoolattendance <- as.data.frame(count)

# Rename the columns for clarity
names(count_schoolattendance) <- c("type", "count")

# Calculate percentages
count_schoolattendance <- count_schoolattendance %>%
  mutate(
    percentage = count / sum(count) * 100,
    label = paste0(type, ": ", count, " (", round(percentage, 1), "%)")
  )

# Create the plot
ggplot(count_schoolattendance, aes(x = "", y = count, fill = type)) +
  geom_bar(width = 1, stat = "identity", color = "black") +  # Create a bar plot
  coord_polar("y") +  # Convert the bar plot to a pie chart
  scale_fill_manual(values = c("green", "orange")) +  # Set custom colors for the fill
  labs(
    title = "Percentage of PWDs Who Attended School",  # Update the plot title
    x = NULL,  # Remove x-axis label
    y = NULL,  # Remove y-axis label
    fill = "Category"  # Legend title
  ) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "black")  # Add labels with count and percentage

```
The pie graph above represents the percentage of PWDs who attended school, represented by the binary variable 1, and the percentage of PWDs who did not attend school, represented by binary variable 0. It could be seen that 89.1% of the respondents, which corresponds to 302 PWDs from Barangay CAA, has attended school or is still attending to school. This is a substantial majority that may indicate accessibility of education to PWDs within the community. However, 10.9% of the PWDs have failed to attend school, highlighting a gap in educational attendance. But despite the significantly large portion of the population who have attended school, this does not equate student retention, nor quality education.

### \[1.2\] Current enrollment

### \[1.3\] School category

------------------------------------------------------------------------

## OBJECTIVE 2 \| Identify the barriers

### \[2.1\] Nonattendance

### \[2.2\] Nonenrollment

------------------------------------------------------------------------

## OBJECTIVE 3 \| Evaluate the accessibility

### **\[3.1\] Descriptive**

#### \[3.1.1\] Years of Schooling

#### \[3.1.2\] Type of Schooling

### **\[3.2\] Statistic**

#### \[3.2.1\] ANOVA

#### \[3.2.2\] Regression
