---
title: "[ECODEVT] Data Analysis"
author: "Group 1"
date: today
format: 
  html:
    toc: true
    theme: united
    embed-resources: true
knitr:
  opts_chunk: 
    warning: false
    message: false
editor: visual
---

# Paper Details

## **Research Question**

Are the current Philippine education system and alternative training programs adequate to cater to the educational and physiological needs of persons with disabilities (PWDs) in Barangay CAA?

## **Statement of Hypothesis**

Ho: The regular schooling and alternative learning system for PWDs in Barangay CAA is accessible.

Ha: The regular schooling and alternative learning system for PWDs in Barangay CAA is inaccessible.

## **Research Objectives**

-   Illustrate the school attendance of PWDs

-   Identify the barriers experienced by PWDs in the education system

-   Evaluate the accessibility of regular schools and ALS programs in accommodating various disabilities

------------------------------------------------------------------------

# Preliminary Steps

## Install and load the necessary data sets

```{r}

```

## Install and load R packages

Make sure that the system has access to the *tidyverse*, *psych,* and *readxl* packages needed for data management, and the *car, broom, lmtest,* *whitestrap,* and *wooldridge* needed for regression models.

```{r}
# Install three packages that are not yet installed
if(!("tidyverse" %in% installed.packages()[,"Package"])) install.packages("tidyverse")
if(!("readxl" %in% installed.packages()[,"Package"])) install.packages("readxl")
if(!("psych" %in% installed.packages()[,"Package"])) install.packages("psych")
if(!("car" %in% installed.packages()[,"Package"])) install.packages("car")
if(!("broom" %in% installed.packages()[,"Package"])) install.packages("broom")
if(!("lmtest" %in% installed.packages()[,"Package"])) install.packages("lmtest")
if(!("whitestrap" %in% installed.packages()[,"Package"])) install.packages("whitestrap")
if(!("wooldridge" %in% installed.packages()[,"Package"])) install.packages("wooldridge")

library(tidyverse)
library(readxl)
library(psych)
library(car)
library(broom)
library(lmtest)
library(whitestrap)
library(wooldridge)
library(ggplot2)
```

------------------------------------------------------------------------

## OBJECTIVE 1 \| Illustrate the school attendance of PWDs

### \[1.1\] School attendance

### \[1.2\] Current enrollment

### \[1.3\] School category

------------------------------------------------------------------------

## OBJECTIVE 2 \| Identify the barriers

### \[2.1\] Nonattendance

### \[2.2\] Nonenrollment

------------------------------------------------------------------------

## OBJECTIVE 3 \| Evaluate the accessibility

### **\[3.1\] Descriptive**

#### \[3.1.1\] Years of Schooling

#### \[3.1.2\] Type of Schooling

### **\[3.2\] Statistic**

#### \[3.2.1\] ANOVA

#### \[3.2.2\] Regression
